Arbius: A Decentralized Machine Learning Network with Economic Incentive

### 2024-02-04 paper/paper.tex
paper updates

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={blue},
    citecolor={blue},
    urlcolor={blue}
}
\usepackage[natbib=true, style=numeric,sorting=none]{biblatex}
\addbibresource{bibliography.bib}
\usepackage[title]{appendix}

\title{Arbius: A Decentralized Machine Learning Network with Economic Incentive}
\author{Kasumi}
\date{October 2023}

@@

A peer-to-peer hybrid proof-of-work/proof-of-stake token (AIUS) based on reproducible computation allows anyone in the world to serve and request AI models without requiring a trusted third party. Such a system is capable of producing results such as Stable Diffusion \cite{stablediffusion} image generation with low latency overhead and competitive fees to centralized providers. Models are able to accrue fees into smart contracts, providing a decentralized a way for creators to generate income from utility and usage of their work. Censoring models is economically infeasible, allowing for truly unstoppable AI systems.

@@

To create a task a user prepares input data for the task and submits a transaction containing the model and the input data. along with an optional fee (paid in AIUS) to the blockchain. The IPFS\cite{benet2014ipfs} Content Identifier (CID) is calculated by a smart contract and stored, miners may automatically mirror the input data.

@@

\begin{enumerate}
    \item User formats a task request
    \item User broadcasts a transaction calling createTask and attaches a fee
    \item Contract calculates CID of input data and stores it
    \item Solvers that are scanning for tasks download the request data
    \item Solvers run associated model using user's input and a seed derived from the task and system state
    \item Solvers pin model response to IPFS and broadcast a commitment transaction referencing the task and response hash
    \item Solvers broadcast a solution referencing the task, commitment, and solution data. The first solution proposed wins.
    \item The user is scanning for solutions to their task, and when they see one they can use the result immediately or wait for claim period to ensure other solvers did not contest.
    \item The winning solver waits for a period of time to allow for other solvers to contest the solution, prior to being able to claim the task fee and any task reward.
\end{enumerate}

@@

\begin{enumerate}
    \item Solver contests a solution referencing its task id
    \item Other solvers are scanning for new contestations, and choose to verify the task was completed accurately by the solution submitter
    \item Solvers vote over a period of time on whether the contestation was valid.
    \item When the voting period is finished, the winning voters receive the losing voters slashed funds, and the task submitter gets refund if solution submitter was determined to provide an inaccurate result.
\end{enumerate}

More details about contestations can be found in \ref{contestation}.

\subsection{Task Reward} \label{taskreward}

@@

Task rewards works similarly to how difficulty in Bitcoin \cite{bitcoin} adjusts the work required to mine a block to target an emission schedule, we adjust the reward amount per task to target our emission schedule(\ref{tokenomics} for schedule).

@@

Machine learning models may be registered permissionlessly. Each model references a docker container which follows a standard Cog \cite{cog} interface for interacting with it. This allows great flexibility in the types of models that can be run, and importantly, allows each run to be reproducible.

@@

Models can optionally have a flat-fee they charge for each use, which accrues in the models specified address. This allows models to operate as DAOs, with their own token dynamics decided by their respective teams. A simple case would be to have the fees accrued be distributed pro-rata to holders of the DAO.

@@

Once complete, solvers upload the result to IPFS and save the CID. Then they submit a commitment containing a hash of their solution in order to prevent others from stealing their work by watching the mempool (or sequencer queue or similar). Once the commitment is confirmed, they can safely broadcast their transaction referencing the task and their solution CID. The task is now locked from others submitting.

\subsection{Contestation} \label{contestation}

@@

\section{Tokenomics} \label{tokenomics}

@@

\begin{itemize}
    \item 1\% Initial Liquidity
    \item 9\% Liquidity Incentives (\approx 4 year vesting)
    \item 10\% DAO (\approx 4 year vesting)
    \item 10\% Team (4 year vesting)
    \item 10\% Private sale (2 year vesting)
    \item 60\% Mining (\approx 7 year emission schedule)
\end{itemize}

\subsection{DAO}

10\% of all tokens are sent to the Arbius DAO treasury. These tokens are to be utilized by the DAO for future development and promotion of the protocol. The soft target is to have DAO funds cover at least 4 years of development, with the goal of having the DAO be self-sustaining by the end of the 4 year period.

@@

Initially 10k AIUS(1\% of total supply) and \$30k of ETH will be used to create a Uniswap pool. The remaining 9\% will be used to incentivize liquidity providers. Users will be able to stake and bond liquidity in order to receive AIUS rewards. The 9\% will be distributed over 4 years, with the first year having the highest rewards. Of the 9\%(90k AIUS), rewards are expected to be deployed between LP Rewards / Bonds as follows:

@@

Mining is covered with a time based target total supply of $600000(1-{0.5^{y})}$ where y is year. After 1 year, there should be approximately 300k tokens minted, and after 2 years approximately 450k tokens minted. After 7 years approximately 99\% of tokens should be minted.

The real emission rate (recall \ref{taskreward}) will be slightly faster than the target emission rate, due to the variable task reward. However, it is unlikely to be much more than 10\% faster due to the exponential falloff of task rewards. 10\% greater total supply than expected total supply by time results in a 1024-fold reduction of task rewards.

@@

All contracts and treasury are owned by a governor contract which implements Bravo \cite{bravo} style voting. An initial quorum requirement of 4\%, a 1 day voting delay for proposals, and 1 week voting period are set as the initial parameters. These and all other parameters and upgrades can be voted upon by the token holders.

@@

We choose Arbitrum Nova \cite{arbitrumnitro}. Arbitrum Nova is a Layer 2 optimistic rollup built on top of Ethereum. Nova has near-instant confirmation times, greatly reduced gas fees, and is the most decentralized given our low fee requirement.

@@

\printbibliography

@@

We already see the early stages of autonomous AI with technologies such as BabyAGI and Auto-GPT. While it is impossible to predict how fast these will evolve and become capable of living independently of humans, it is inevitable, and quickly approaching.

>>>>

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\hypersetup{colorlinks, linkcolor={blue}, citecolor={blue}, urlcolor={blue}}
\usepackage[natbib=true, style=numeric,sorting=none]{biblatex}
\addbibresource{bibliography.bib}
\usepackage[title]{appendix}

\title{Arbius: A Decentralized Machine Learning Network with Economic Incentive}
\author{Kasumi}
\date{January 2023}

@@

The Arbius token (AIUS) is mineable and based on a new Proof-of-AI-Compute algorithm. It incentivizes reproducible computation allowing anyone in the world to serve and request AI models without requiring a trusted third party. Such a system is capable of producing results such as Stable Diffusion\cite{stablediffusion} image generation with low latency overhead and competitive fees to centralized providers. Models are able to accrue fees into smart contracts, providing a decentralized way for creators to generate income from utility and usage of their work. Censoring models is economically infeasible, allowing for truly unstoppable AI systems.

@@

To create a task a user prepares input data for the task and submits a transaction containing the model and the input data, along with an optional fee (paid in AIUS) to the blockchain. The IPFS\cite{benet2014ipfs} Content Identifier (CID) is calculated by a smart contract and stored, miners may automatically mirror the input data.

@@

\begin{enumerate}
    \item User formats a task request.
    \item User broadcasts a transaction calling createTask and attaches a fee.
    \item Contract calculates CID of input data and stores it.
    \item Solvers that are scanning for tasks download the request data.
    \item Solvers run associated model using user's input and a seed derived from the task and system state.
    \item Solvers pin model response to IPFS and broadcast a commitment transaction referencing the task and response hash.
    \item Solvers broadcast a solution referencing the task, commitment, and solution data. The first solution proposed wins.
    \item The user is scanning for solutions to their task, and when they see one they can use the result immediately or wait for claim period to ensure other solvers did not contest.
    \item The winning solver waits for a period of time to allow for other solvers to contest the solution, prior to being able to claim the task fee and any task reward.
\end{enumerate}

@@

\begin{enumerate}
    \item Solver contests a solution referencing its task id.
    \item Other solvers are scanning for new contestations, and choose to verify the task was completed accurately by the solution submitter.
    \item Solvers vote over a period of time on whether the contestation was valid.
    \item When the voting period is finished, the winning voters receive the losing voters slashed funds, and the task submitter gets refund if solution submitter was determined to provide an inaccurate result.
\end{enumerate}

More details about contestations can be found in~\ref{contestation}.

\subsection{Task Reward}\label{taskreward}

@@

Task rewards works similarly to how difficulty in Bitcoin\cite{bitcoin} adjusts the work required to mine a block to target an emission schedule, we adjust the reward amount per task to target our emission schedule~(\ref{tokenomics} for schedule).

@@

Machine learning models may be registered permissionlessly. Each model references a docker container which follows a standard Cog\cite{cog} interface for interacting with it. This allows great flexibility in the types of models that can be run, and importantly, allows each run to be reproducible.

@@

Models can optionally have a flat-fee they charge for each use, which accrues in the models specified address. This allows models to operate as DAOs, with their own token dynamics decided by their respective teams. A simple case would be to have the fees accrued be distributed pro-rata to holders of the DAO\@.

@@

Once complete, solvers upload the result to IPFS and save the CID\@. Then they submit a commitment containing a hash of their solution in order to prevent others from stealing their work by watching the mempool (or sequencer queue or similar). Once the commitment is confirmed, they can safely broadcast their transaction referencing the task and their solution CID\@. The task is now locked from others submitting.

\subsection{Contestation}\label{contestation}

@@

\section{Tokenomics}\label{tokenomics}

@@

\begin{itemize}
    \item 1\% Initial DEX Liquidity
    \item 9\% DEX Liquidity Provider Incentives ($\approx4$ year vesting)
    \item 10\% DAO ($\approx4$ year vesting)
    \item 10\% Team (4 year vesting)
    \item 10\% Private sale (2 year vesting)
    \item 60\% Mining ($\approx7$ year emission schedule)
\end{itemize}

\begin{figure}[h]
\caption{Total supply curve}
\centering
\includegraphics[width=0.9\textwidth]{combined}
\end{figure}

\begin{figure}[h]
    \caption{Supply curve components}
\centering
\includegraphics[width=1.0\textwidth]{separate}
\end{figure}

\newpage
\subsection{DAO}

10\% of all tokens as well as 10\% of task fees are sent to the Arbius DAO treasury. These tokens are to be utilized by the DAO for future development and promotion of the protocol. The soft target is to have DAO funds cover at least 4 years of development, with the goal of having the DAO be self-sustaining by the end of the 4 year period.

@@

Initially 10k AIUS (1\% of total supply) and \$30k of ETH will be used to create a Uniswap pool. This equates to \$3 per token, \$3m~FDV, the same valuation as provided to the private sale investors. The remaining 9\% will be used to incentivize liquidity providers. Users will be able to stake and bond liquidity in order to receive AIUS rewards. The 9\% will be distributed over 4 years, with the first year having the highest rewards. Of the 9\%(90k AIUS), rewards are expected to be deployed between LP Rewards / Bonds as follows:

@@

Mining is covered with a time based target total supply of $600000(1-{0.5^{y}})$ where y is year. After 1 year, there should be approximately 300k tokens minted via mining, and after 2 years approximately 450k tokens minted. After 7 years approximately 99\% of tokens should be minted.

The real emission rate (recall~\ref{taskreward}) will be slightly faster than the target emission rate, due to the variable task reward. However, it is unlikely to be much more than 10\% faster due to the exponential falloff of task rewards. 10\% greater total supply than expected total supply by time results in a 1024-fold reduction of task rewards.

\subsection{Economic Incentive}

@@

All contracts and treasury are owned by a governor contract which implements Bravo\cite{bravo} style voting. An initial quorum requirement of 4\%, a 1 day voting delay for proposals, and 1 week voting period are set as the initial parameters. These and all other parameters and upgrades can be voted upon by the token holders.

@@

We choose Arbitrum Nova\cite{arbitrumnitro}. Arbitrum Nova is a Layer 2 optimistic rollup built on top of Ethereum. Nova has near-instant confirmation times, greatly reduced gas fees, and is the most decentralized given our low fee requirement.

@@

\printbibliography{}

@@

We already see the early stages of autonomous AI with technologies such as Auto-GPT\@. While it is impossible to predict how fast these will evolve and become capable of living independently of humans, it is inevitable, and quickly approaching.
